mir\_eval

### 2014-05-06 paper/paper.tex
Filled out table

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c}
\toprule
 \multicolumn{9}{ c }{Beat Tracking} \\
  \cmidrule(lr){1-9}
 F-Measure  &  Cemgil   &   Goto    &    P-score & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
 0.00659 & 0.00035 & 0.00060  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
  \midrule
 \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{4}{ c }{Something else}  \\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-9}
 Root  &  Maj/Min   &   Maj/Min + Inv    &     Sevenths     &     Sevenths + Inv & CMLt      &   AMLc     &     AMLt    &      D (bits)\\
 ??? & ??? & ???  & ??? & ??? & 0.00135 & 0.00137&  0.00135 & 0.10566\\
  \midrule
 \multicolumn{3}{ c }{Onset Detection} & \multicolumn{6}{ c }{Blah}  \\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-9}
 F-Measure  &  Precision   &  Recall    &     McKinney P-s & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
 0.00203 & 0.00202 & 0.00203  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
  \bottomrule

>>>>

% Beat - 9 metrics
% Chord - 5 metrics
% Segmentation - 14 metrics
% Melody - 5 metrics
% Pattern - 21 metrics
% Onset - 3 metrics
% Source Separation - 3 metrics

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c c}
\toprule
 \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){5-10}
 Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
 ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \midrule
 \multicolumn{10}{ c }{Segmentation} \\
  \cmidrule(lr){1-10}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
  \midrule
 \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-10}
  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
  \midrule
 \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-10}
  AMLc       & AMLt       & D (bits) & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
  0.137\% &    0.139\% &   10.166\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{10}{ c }{Pattern}\\
  \cmidrule(lr){1-10}
  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-7}
  \cmidrule(lr){8-10}
 Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
 ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
  \bottomrule
